Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii–-Moriya interactions in antiferromagnetic insulators

### 2019-02-12 Paper/paper.tex
Relabel

\begin{align}
\label{MKMHeff0}
&\hat{H}_{\text{eff}}^0 = \sum_{\langle i,j \rangle} J_{1,ij}^0\bs{S}_i\cdot\bs{S}_j +\n \\
&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}^0\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}^0\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}^0 \bs{S}_j \right\}
\end{align}

@@

\begin{align*}
J_{1,ij}^0 &= 2t_1^2 \\
J_{2,ij}^0 &= 2t_2^2 \\
\bs{D}_{2,ij}^0 &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \\
\bs{\Gamma}_{2,ij}^0 &= 2\Delta^2 \text{diag}(-1,-1,1)
\end{align*}

@@

\begin{align*}
J_{1,ij} &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
J_{2,ij} &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
\bs{D}_{2,ij} &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
\bs{\Gamma}_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
\end{align*}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}}{J_{1,ij}^0}$ and $\tilde{D}_{2} = \frac{D_{2,ij}}{D_{2,ij}^0}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.

@@

\begin{align*}
J_{1,ij} &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
J_{2,ij} &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
\bs{D}_{2,ij} &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
\bs{\Gamma}_{2,ij} &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
\end{align*}

>>>>

\begin{align}
\label{MKMHeff0}
&\hat{H}_{\text{eff}} = \sum_{\langle i,j \rangle} J_{1,ij}\bs{S}_i\cdot\bs{S}_j +\n \\
&+ \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}\bs{S}_i\cdot\bs{S}_j + \bs{D}_{2,ij}\cdot \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j \right\}
\end{align}

@@

\begin{align*}
J_{1,ij} &= 2t_1^2 \\
J_{2,ij} &= 2t_2^2 \\
\bs{D}_{2,ij} &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \\
\bs{\Gamma}_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1)
\end{align*}

@@

\begin{align*}
J_{1,ij}' &= 2t_1^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
J_{2,ij}' &= 2t_2^2\frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
\bs{D}_{2,ij}' &= - 4\nu_{ij} t_2 \Delta \hat{e}_z \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega} \\
\bs{\Gamma}'_{2,ij} &= 2\Delta^2 \text{diag}(-1,-1,1) \frac{\mathcal{J}_{n}^2(\alpha_{ij})}{\text{U}+n\omega}
\end{align*}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{../Figures/NNvsNNN.pdf}
\caption{For circularly polarized light we obtain $\tilde{J}_1 = \frac{J_{1,ij}'}{J_{1,ij}}$ and $\tilde{D}_{2} = \frac{D_{2,ij}'}{D_{2,ij}}$ as function of $\mathcal{E} = \frac{eaE_0}{\omega}$, where $e$ is the electron charge and $a$ is the lattice constant. The results are obtain for (units of $\hbar=t_1=1$) $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6, 16$. Solid lines are for $\omega = 6$ and dashed lines are for $\omega = 16$. For $\tilde{J}_1$, similar results are obtained by Mentink et Al. \cite{Mentink2015}.}
\label{fig2}
\vspace*{-6pt}
\end{figure}
A similar Hamiltonian including a NN exchange term and a NNN DMI term was first proposed by S. A. Owerre to model honeycome topological magnon insulators \cite{Owerre2016} \cite{Elyasi}. Additionally, experimental results regarding topological properties of spin waves in honeycomb ferromagnet Cr$I_3$ can only be understood by considering this Hamiltonian \cite{Chen2018}. This model is also relevant for the study of Spin Hall effects of Weyl magnons \cite{Zyuzin2018} \cite{Sekine2015}.

@@

\begin{align*}
J_{1,ij}' &= \frac{2t_1^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
J_{2,ij}' &= \frac{2t_2^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2} \\
\bs{D}_{2,ij}' &= -\frac{4\nu_{ij} t_2 \Delta \text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\hat{e}_z \\
\bs{\Gamma}_{2,ij}' &= \frac{2\Delta^2\text{U}}{\text{U}^2-(\epsilon_j-\epsilon_i)^2}\text{diag}(-1,-1,1)
\end{align*}
